---
title: 'Mock Pratical '
author: "Guoxin Li"
output: word_document
---

```{r,echo=FALSE}
# load data
caffe = read.csv("I:/Oxford/R Data/caffeine.csv")
```


```{r, echo=FALSE}
summary(caffe)
apply(caffe,2,sd)
```
The standard deviations of each groups are almost same. From the summary table of the three group of the students, we can see that all the statistical metrics show that the different dose of caffeine affects performance of taps per minute. We also can see the more caffeine usage, the more affects of the taps. But we need a further test to the relation between dose of caffeine and taps per minute.

we also do the virtualization of the data, we do a boxplot of three groups
```{r, echo=FALSE}
boxplot(caffe,xlab = "Groups",ylab = "taps/minute",main = "Caffeine Data")
```

From the boxplot, it gives a strong picture of what we find in previous step.

```{r, echo=FALSE}
library(lattice)
new_caffe = as.data.frame(cbind(c(caffe$None,caffe$Caff.100ml,caffe$Caff.200ml), factor(rep(c(1,2,3),each = 10))))
names(new_caffe) = c("taps", "groups")
histogram(~taps|factor(new_caffe$groups), data = new_caffe, main = "Caffeine Data")
```

The histogram of the caffeine data shows that as the does of the caffeien increasing, the distribution of the taps becomes more and more left skewed

Now we are starting to the hypothesis test to give a statistical evidence of the effect of the caffeine.
Before we doing the test, first need to check if the data follow the normality assumption. we use qqplot to draw the data of None group and 100ml Caffeien group.
```{r, echo=FALSE}
#check normality
qqnorm(caffe$None, xlab = "Teoretical Quantiles of None group")
qqline(caffe$None)

qqnorm(caffe$Caff.100ml,xlab = "Teoretical Quantiles of 100ml caffeine")
qqline(caffe$Caff.100ml)
```

From the qqplot, we can see that 100ml caffeine group is almost normally distributed sinece all the points almost on the straight line. But for the None group, we can see the lower quantile and higher are far away from the straight line, so the None group data may have a heavy tail of the normal distribution data. From the qqplot general we can say that two groups of data are almost normally distributed, so we can start to do hypothesis test on the data.

For testing the affects of the performance between None group and 100ml Caffeine group, we set up the T-test and our null hypothesis test is the caffeine won't affect tapping speed, and the alternative hypothesis test is the caffeine will increasing the tapping speed. The null hypothesis test equal to the mean of 100ml caffeine - the mean of None caffeine is 0, the alternative is the difference between caffeine group and None group is greater than 0. We set our alpha value is 0.05 
```{r, echo=FALSE}
# difference of the tap between two groups
test = caffe$Caff.100ml - caffe$None
t.test(test, alternative = "greater", mu = 0)
```
From the T-test, the p-value is 0.04128, which is less than 0.05, so we reject the null hypothesis, we conclude that the 100ml caffeine increasing the tapping speed compare with the group without taking caffeine.

For the same hypothesis test, now we use wilcox test to test it again.
```{r, echo=FALSE}
wilcox.test(test, alternative = "greater", mu = 0)

```
The p-value is 0.00482, which is less than 0.05, so the wilcox test gives us a same result as T-test.

Since we reject the null hypothesis, now we are looking at the power of the t-test, which is the reject the null hypothesis when the alternative is true.
```{r,echo=FALSE}
power.t.test(n = 10, delta = 1.6, sd = 2.2, sig.level = 0.05)

power.t.test(n = 31, delta = 1.6, sd = 2.2, sig.level = 0.05)
```
If we look at the power of the T-test that we did on previous step, the power is 0.337 which is very small compare to 0.8(general value). Even we rejce the null hypothesis test os statistical significance, but the small power of the test gives us a warning which is the sample size of the data is not big enough.If under the same assumption, we need at least 31 students in each group to obtain a power at 0.8. So for give a confidence conclusion of the effect of caffeine, we need more sample data.











Now we are starting to the hypothesis test to give a statistical evidence of the effect of the 200ml caffeine.
Before we doing the test, we also need to check if the data follow the normality assumption. we use qqplot to draw the data of None group and 200ml Caffeien group.
```{r, echo=FALSE}
#check normality
qqnorm(caffe$None)
qqline(caffe$None)

qqnorm(caffe$Caff.200ml)
qqline(caffe$Caff.200ml)
```

From the qqplot, we can see that 200ml caffeine group is almost normally distributed sinece all the points almost on the straight line. From the qqplot general we can say that two groups of data are almost normally distributed, so we can start to do hypothesis test on the data.

For testing the affects of the performance between None group and 200ml Caffeine group, we set up same T-test as we test 100ml caffeine 
```{r, echo=FALSE}
# difference of the tap between two groups
test = caffe$Caff.200ml - caffe$None
t.test(test, alternative = "greater", mu = 0)
```
From the T-test, the p-value is 0.0008388, which is less than 0.05, so we reject the null hypothesis, we conclude that the 200ml caffeine increasing the tapping speed compare with the group without taking caffeine.

For the same hypothesis test, now we use wilcox test to test it again.
```{r, echo=FALSE}
wilcox.test(test, alternative = "greater", mu = 0)

```
The p-value is 0.0044423, which is less than 0.05, so the wilcox test gives us a same result as T-test.

Since we reject the null hypothesis, now we are looking at the power of the t-test, which is the reject the null hypothesis when the alternative is true.
```{r,echo=FALSE}
power.t.test(n = 10, delta = 1.6, sd = 2.2, sig.level = 0.05)

power.t.test(n = 31, delta = 1.6, sd = 2.2, sig.level = 0.05)
```
For the power of test, we are in the same situation as we test for 100ml caffeine gourp.If under the same assumption, we need at least 31 students in each group to obtain a power at 0.8. So for give a confidence conclusion of the effect of caffeine, we need more sample data.